### 2018-01-23 ApproxComp/sec-beyond.tex

\section{Beyond Query and Data Approximations}
\label{sec-beyond}

@@

Data partitioning, Data indexing and Distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.

>>>>

\section{Beyond Query and Data Approximations}
\label{sec-beyond}
No One-Size-Fits-All

@@

Techniques such as data partitioning, data indexing, distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.

### 2018-01-23 ApproxComp/sec-introduction.tex

1. history  of big data - governmental policy.

%2012年3月29日，美国总统科技政策办公室OSTP（Office of Science and Technology Policy）宣布了每年投资两亿美元的“大数据研究计划”（Big Data R&D Initiative）
%同天，我国科技部发布的“‘十二五’国家科技计划信息技术领域2013年度备选项目征集指南”把“大数据研究”列在首位

%美国2016年5月发布《联邦大数据研究与开发战略计划》
%其目标是对联邦机构的大数据相关项目和投资进行指导,主要围绕代表大数据研发关键领域的七个战略进行，包括促进人类对科学、医学和安全所有分支的认识;确保美国在研发领域继续发挥领导作用；通过研发来提高美国和世界解决紧迫社会和环境问题的能力。

2. progress of applications of big data techniques

3. (machine learning, systems -hadoop, spark)

A fundamental issue for big data analytics is the efficiency. There are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.  In this article, we present the idea of two classes of techniques for efficient and effective big
data analytics: query approximation and data approximation, based on our recent research. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation techniques that we are going to introduce are not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.

~\cite{MaLHLH16}

@@

https://cacm.acm.org/about-communications/author-center/author-guidelines

>>>>

Over the past a few years, research and development progresses on big data analytics have made significant achievements with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}. A fundamental issue for big data analytics is the efficiency, and there are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.  In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation techniques that we are going to introduce are not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.

\section{Key Insights}
\label{sec-insight}

contributions and summary of results

\eat{
Contributed Articles cover the wide and abundant spectrum of the computing field¡ªits open challenges, technical visions and perspectives, educational aspects, societal impact, significant applications and research results of high significance and broad interest. Following the roots of Communications, these submissions are peer-reviewed to ensure the highest quality. Topics covered must reach out to a very broad technical audience. While articles appearing in an ACM Transactions journal are aimed at a specialized audience, articles in Communications should be aimed at the broad computing and information technology community.

A Contributed Article should set the background and provide introductory references, define fundamental concepts, compare alternate approaches, and explain the significance or application of a particular technology or result by means of well-reasoned text and pertinent graphical material. The use of sidebars to illustrate significant points is encouraged.

@@

Submissions to the Contributed Articles section should be accompanied by a cover letter indicating:

? Title and the central theme of the article;
? Statement addressing why the material is important to the computing field and of value to the Communications reader; and,
? Names and email addresses of three or more recognized experts who would be considered appropriate to review the submission.

%https://cacm.acm.org/about-communications/author-center/author-guidelines

%Lionel M. Ni
%Elisa Bertino
%Yannis Ioannidis

}

### 2018-01-23 ApproxComp/sec-query.tex

\stitle{(1) Strong simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
{\em Graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.

@@

\stitle{(3) One-pass Trajectory Compression~\cite{LinMZWH17}}. Nowadays, various sensors are collecting, storing and transmitting
tremendous trajectory data, and it is known that raw trajectory data seriously wastes the storage, network
band and computing resource.  Trajectory Compression techniques are an effective approach to attacking this issue by
compressing data points in a trajectory to a set of continuous
line segments, and are commonly used in practice.

 Though lossless compression methods have no information loss, their compression ratios are poor and queries on the compressed data are time consuming because data reconstructions from the compressed data are typically needed before the queries \cite{Nibali:Trajic} .
Hence, A large number of lossy trajectory compression techniques, most notably the piece-wise line simplification, have been developed.
These techniques focus on good compression ratios with bounded errors, and are the mainstream techniques for trajectory compression.
The idea of piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant. It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

The \lsa algorithms solving the \emph{min-$\#$} problem fall into two categories: {\em optimal} and {\em sub-optimal}.
The \textit{optimal} methods\cite{Imai:Optimal} are to find the minimal number of points or segments to represent the original polygonal lines \wrt an error bound $\epsilon$. The optimal \lsa algorithms have relative high time/space complexities which make them impractical for large trajectory data.
Hence, \textit{sub-optimal} \lsa algorithms have been developed and/or introduced for trajectory compression, including batch algorithms (\eg \cite{Douglas:Peucker}), online algorithms (\eg~\cite{Liu:BQS}) and one-pass algorithms (\eg~\cite{LinMZWH17}).

 We first develop a one-pass error bounded trajectory simplification algorithm that runs in $O(n)$ time and $O(1)$ space. \operb is based on a novel local distance checking method, and equipped with five optimization techniques to further improve its compression ratio. Essentially, fitting function: property...

\stab (2) We then propose an aggressive one-pass error bounded trajectory simplification algorithm (\operab) that remains in $O(n)$ time and $O(1)$ space.
\operba allows interpolating new data points into a trajectory under certain conditions and with practical considerations. The rational lies in that moving objects  have sudden track changes while data points may  not be sampled due to various reasons.

 finally conduct an extensive experimental study, by comparing our algorithms \operaa and \operab with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}). We find that \operaa and \operab are on average $(4.1, 4.1, 5.4, 5.2)$ times faster than \fbqsa on , respectively.
For compression ratios, \operaa is comparable with \dpa, and \operab is better than \dpa that is on average ($84.2\%, 86.4\%, 97.1\%, 94.7\%$) of \dpa , respectively.

@@

 a highly efficient and effective data-driven approach, instead of filter-and-verification, which employs hidden data statistics to find dense temporal subgraphs in large temporal networks.  data-driven approach to identifying $k$ time intervals from a total of $T*(T+1)/2$ ones, striking a balance between quality and efficiency, in which $T$ is the number of snapshots and $k$ is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}.

>>>>

\stitle{(1) Strong Simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
{\em Graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.

@@

\stitle{(3) One-Pass Trajectory Compression~\cite{LinMZWH17}}.  Trajectory compression (also known as trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.

Though lossless compression methods incur no information loss, their compression ratios are typically poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}. Hence, lossy techniques become the mainstream for trajectory compression,
which provide approximate solutions with good compression ratios and bounded errors.

Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant. It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

\lsa algorithms fall into two categories: {\em optimal} and {\em approximate}.
Optimal methods\cite{Imai:Optimal} are to find the minimum number of points or segments to represent the original polygonal lines \wrt an error bound $\epsilon$. They have higher time and space complexities, and are not practical for large trajectory data.
Hence,  various approximate \lsa algorithms have been developed, from batch algorithms (\eg \cite{Douglas:Peucker}) to online algorithms (\eg~\cite{Liu:BQS}) and to one-pass algorithms (\eg~\cite{LinMZWH17}).

An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing, and
the difficulty comes from the need to achieve effective compression ratios.
Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker} and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window. That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed. Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.

 We develop a  fitting function such that a data point is checked only once during the entire process of trajectory simplification. Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once. By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}). We find that algorithms are more than four times faster than \fbqsa, and have  comparable compression ratios with \dpa.

@@

 a highly efficient and effective data-driven approach, instead of filter-and-verification, which employs hidden data statistics to find dense temporal subgraphs in large temporal networks.  data-driven approach to identifying $k$ time intervals from a total of $T*(T+1)/2$ ones, striking a balance between quality and efficiency, in which $T$ is the number of snapshots and $k$ is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
